results_so_far

### 2022-02-25 presentation_example.Rmd
add analyses and example rmd uses

---
title: "How do changes in ex vary between countries?"
author: "Jon Minton"
date: "22/02/2022"
output:
  word_document: default
  html_document: default
---

# Introduction

This notebook will compare annual changes in life expectancy at both birth ($e_0$) and at age 65 ($e_{65}$) in the UK and UK nations, with other select European nations, including a 'Synthetic Germany' created from a weighted average of East and West German data for common years. The method for creating this 'Synthetic Germany' is also described in this and linked documents.

@@

# Methods

@@

Data were extracted from the [Human Mortality Database](https://mortality.org/) via the R package [`HMDHFDplus`](http://www.demogr.mpg.de/en/projects_publications/publications_1904/mpidr_technical_reports/reading_human_fertility_database_and_human_mortality_database_data_into_r_5438.htm).

The following countries are included in the comparison:

@@

# Results

## Descriptive Results /Starter Eyeballing

### Life expectancy trends

The following shows life expectancy at birth and at age 65 for selected nations:

Here it is at birth...

@@

Here it is at age 65

@@

Some insightful comment about what's going on.

Scotland looks pretty bad compared with the other countries.

## Change in life expectancy in these nations

```{r}
change_in_ex_selected_countries <- 
  hmd_ex_selected_countries %>% 
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(delta_ex = ex - lag(ex)) %>% 
    ungroup()

change_in_ex_selected_countries
```

```{r}
change_in_ex_selected_countries %>% 
  filter(between(year, 1980, 2020)) %>% 
  ggplot(aes(x = year, y = delta_ex)) + 
  geom_point(alpha = 0.2) + 
  stat_smooth() + 
  facet_grid(code~sex) + 
  geom_hline(yintercept = 0)

# Discussion

# Bibliography

>>>>

---
title: "results_so_far"
author: "Jon Minton"
date: "24/02/2022"
output: ioslides_presentation
---

@@

@@

@@

## Life expectancy at birth

@@

## life expectancy at age 65

@@
